---
title: "xxxxx Disease Outbreak"
subtitle: "Daily situation report"
author: " "
date: 'Produced on `r format(Sys.Date(), "%Y-%m-%d")`'
output:
  html_document:
    self-contained: TRUE
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    number_sections: true
    theme: lumen
params:
  data_date:
    label: "Date of data:"
    value: "2022-12-05"
    input: date
---


```{r include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,  # hide all code chunks in output
  warning = FALSE, # do not show warnings in the output word doc 
  message = FALSE, # do not show  messages in the output word doc
  fig.align = "center", # align all figs in center
  fig.width=8,     # Figure width
  fig.height=4.5,  # Figure height
  fig.topcaption = TRUE  # show figure titles on top of plot
)
```


```{css zoom-lib-src}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img.zoom').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '1200px'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```


```{css}
.header-section-number::after {
content: ".";
}
h2 {
font-size: 23px !important;
}
h3 {
font-size: 18px !important;
}
body {
font-size: 16px !important;
}
.zoomDiv {
  opacity: 0;
  position:absolute;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  box-shadow: 0px 0px 50px #888888;
  max-height:100%; 
  overflow: scroll;
}
.zoomImg {
  width: 1200px;
}
```


```{r}

# install or load packages
pacman::p_load(rio, 
               here, 
               tidyverse, 
               magrittr, 
               janitor, 
               lubridate, 
               skimr, 
               scales, 
               TTR, 
               flextable,
               tidyquant,
               kableExtra,
               formattable,
               gghighlight,
               naniar,
               gt,
               lubridate)



# Set time periods of interest
# database data based on param in YAML
#database_date <- ymd("2022-11-27")
database_date <- ymd(params$data_date)
database_week <- isoweek(database_date)

# Rolling prev x days
prev_1_date <- database_date - 1
prev_7_date <- database_date - 7
prev_14_date <- database_date - 14
prev_21_date <- database_date - 21


# last full week for weekly perc. changes etc.
this_week <- case_when(
  wday(database_date, week_start = 1) >= 5 ~ floor_date(database_date, "week", week_start = 1),
  TRUE ~ floor_date(database_date, "week", week_start = 1) - weeks(1)
)
week_ago <- (this_week - weeks(1))
four_weeks_ago <- (this_week - weeks(4))

# import linelist, needs to be updated to connect to godataR outputs.

linelist <- import(here("data","raw","linelist","filename.xlsx"))

# clean linelist and output into /data/clean folder for subsequent analyses
# needs to be updated to connect to clean godataR outputs.

source(here("scripts","clean_linelist.R"))

```

```{r}
# set themes
source(here("scripts","themes.R"))
```


```{r}
# insert logo here if you have one

# htmltools::img(src = knitr::image_uri(file.path(here::here("inst", "logo.PNG"))), 
#                alt = 'logo', 
#                style = 'position:absolute; top:0; right:0; padding:10px; width:25%')
```

***Daily update : All data as of `r database_date`***

<p>&nbsp;</p>
<p>&nbsp;</p>

The report contains examples of automated epi analyses for use in various\n
presentations or sitreps. Presently, the data sources include x, x and x.\n

<p>&nbsp;</p>
<p>&nbsp;</p>

<!-- overview section -->

```{r, results = 'asis'}
  # knit the document and save the character output to an object
  res <- knitr::knit_child(
    "scripts/key_figures.Rmd",
    quiet = TRUE
  )
  
  # Cat the object to make it render in your main document
  cat(res, sep = '\n')
```


# __Epidemiological Overview__

```{r}

source(here("scripts","epicurve.R"))
plot_epicurve_ma

```


```{r}

source(here("scripts","table_overall.R"))  
print_summary_table

```

## Epidemic curves{.tabset}

### By week of onset
```{r epicurve_ma_week, include=TRUE, fig.align="center"}

source(here("scripts","epicurve.R"))
plot_epicurve_week

```

### By week of reporting
```{r epicurve_ma_week_dor, include=TRUE, fig.align="center"}

source(here("scripts","epicurve.R"))
plot_epicurve_week_dor

```

### By Classification - Sitrep ready
```{r epicurve_by_status_sitrep, include=TRUE, fig.align="center"}

source(here("scripts","epicurve.R"))  
epicurve_by_class_sitrep

```

### By sex
```{r}

source(here("scripts","epicurve.R"))  
epicurve_by_sex
  
```

### By Status
```{r}

source(here("scripts","epicurve.R"))  
epicurve_by_status

```

### By Classification (Daily), Faceted by District
```{r}

source(here("scripts","epicurve.R")) 
epicurve_by_class_district   

```


### By Classification (Weekly), Faceted by District
```{r}

source(here("scripts","epicurve.R")) 
epicurve_by_class_district_week

```

### By Status (Daily), Faceted by District
```{r}

source(here("scripts","epicurve.R")) 
epicurve_by_status_district   

```


### By District (All){.tabset}
```{r}

source(here("scripts","epicurve.R")) 
epicurve_district_all

```

#### Most affected districts
```{r}

source(here("scripts","epicurve.R"))
epicurve_district_highlight

```

#### By district and moving average
```{r}

source(here("scripts","epicurve.R"))        
plot_epicurve_ma_district

```


## Tables{.tabset .tabset-fade .tabset-pills}

### District (last day & total) 
```{r district_table_1d, include = TRUE}

source(here("scripts","table_by_district.R"))
table_district_1d

```


### District (last week & total) 
```{r district_table_7d, include = TRUE}

source(here("scripts","table_by_district.R"))
table_district_7d

```


### District (last week & 21 days) 
```{r district_table_7d_21d, include = TRUE}

source(here("scripts","table_by_district.R"))
table_district_7d_21d

```

### Subcounty (last day & total) 
```{r subcounty_table_1d, include = TRUE}

source(here("scripts","table_by_subcounty.R"))
table_subcounty_1d

```

### Subcounty (last week & total) 
```{r subcounty_table_7d, include = TRUE}

source(here("scripts","table_by_subcounty.R"))
table_subcounty_7d

```


### Subcounty (last week & 21 days) 
```{r subcounty_table_7d_21d, include = TRUE}

source(here("scripts","table_by_subcounty.R"))
table_subcounty_7d_21d

```


<p>&nbsp;</p>
<p>&nbsp;</p>


# __Case characteristics__

## Age/sex breakdown{.tabset}
```{r}

source(here("scripts","age_sex_pyramids.R"))
age_pyramid_case

```

## Occupational breakdown
```{r}

source(here("scripts","occupation.R"))
#case_occupation_pie_chart
cowplot::plot_grid(case_occupation_pie_chart,plot_hcw_type)

```

## Proportion of cases among key age groups over time
```{r}

source(here("scripts","age_sex_pyramids.R"))
cowplot::plot_grid(plot_under5, plot_under18, plot_25_35, nrow = 1 )

```


<p>&nbsp;</p>
<p>&nbsp;</p>

# __Contact tracing performance__
## Contact tracing KPIs over district
```{r}

source(here("scripts","contact_tracing.R"))
formattable_tab_contact_status

```

## Cases who were known contacts
```{r}

source(here("scripts","contact_tracing.R"))
plot_cases_known_contacts

```

<p>&nbsp;</p>
<p>&nbsp;</p>

# __Alerts performance__
## Volume of signals and alerts over time
```{r}

source(here("scripts","alerts.R"))
alert_plot

```


<p>&nbsp;</p>
<p>&nbsp;</p>

# __Transmission dynamics__
## Rt estimates{.tabset}
```{r est_rt, include=TRUE, echo =FALSE, fig.align="center"}

source(here("scripts","Rt_est.R"))
plot_R

```


# __Thematic Areas__

## Case Fatality{.tabset}

### CFR over time
```{r cfr_over_time, include=TRUE, fig.align="center"}

source(here("scripts","cfr_over_time.R"))
plot_cfr_by_week


```

### CFR by admission delay, age, sex
```{r cfr_combined, include=TRUE, fig.align="center"}

source(here("scripts","cfr_plots.R"))
plot_combined_cfr

```

## Time Delays{.tabset}
### Onset to isolation
```{r}

source(here("scripts","time_delays.R"))
boxplot_delay_onset_iso

```

### Onset to sample collection
```{r}

source(here("scripts","time_delays.R"))
boxplot_delay_onset_sample

```

### Contact exposure to isolation
```{r}

source(here("scripts","time_delays.R"))
boxplot_delay_expo_iso

```


### Sample collection to result confirmation
```{r}

source(here("scripts","time_delays.R"))
boxplot_delay_sample_confirmation

```


## Children{.tabset}
### CFR by age group
```{r children_cfr, include=TRUE, fig.align="center"}

source(here("scripts","children_cfr_table.R"))
children_table

```
### CFR by district

## Health care workers{.tabset}
```{r hcw_type, include=TRUE, fig.align="center"}

source(here("scripts","occupation.R"))
plot_hcw_type

```


## Risk factors{.tabset}


# __IPC__

# __Clinical Management__

# __Data quality__

## Data completion - Case investigation{.tabset}

### COmpletion rates across core CIF Variables
```{r linelist_compl, include=TRUE, fig.align="center"}

source(here("scripts","completion.R"))
linelist_compl

```

### Heatmap of % missingness across core CIF Variables
```{r linelist_coml_heat, include=TRUE, fig.align="center"}

source(here("scripts","completion.R"))
linelist_coml_heat

```


## Data completion - Contact tracing

## Data completion - Lab RDS

## Data completion - ETU


# __Forecast/Prepare__
## Case projections{.tabset}
### Scenario 1 (Steady transmission, R0 = 1)
```{r proj_1, include=TRUE, fig.align="center"}

# source(here("scripts","Rt.R"))
# 
# plot_1

```

### Scenario 2 (R0 = 1.2)
```{r proj_2, include=TRUE, fig.align="center"}

# source(here("scripts","Rt.R"))
# 
# plot_1.2

```

### Scenario 3 (Rt = 1.5)
```{r proj_3, include=TRUE, fig.align="center"}

# source(here("scripts","Rt.R"))
# 
# plot_1.5

```


## Estimated Bed needs{.tabset}


